---
title: "workshop analysis code1"
author: "Nak Won Rim"
date: "10/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) # version 1.3.0
library(lmerTest) # version 3.1-1
library(ggpubr) # version 0.2.5
```

```{r load data}
data <- read_csv('processed_data.csv')
```

# first figure: the primacy effect

```{r fig1}
fig1 <- ggplot(data, aes(x=position, y=num_upvotes)) +
  theme_classic() +
  geom_point(alpha=0.4) +
  geom_smooth(method=lm, se=TRUE, level=0.95) +
  labs(x="Position in Thread", y="Number of Upvotes", title="Position and Upvotes")

fig1
```

# second figure: primacy effect are pretty consistent over the quarters

```{r fig2}
fig2 <- ggplot(data, aes(x=position, y=num_upvotes, color=quarter)) +
  theme_classic() +
  geom_point(alpha=0.4) +
  geom_smooth(method=lm, se=TRUE, level=0.95) +
  labs(x="Position in Thread", y="Number of Upvotes", title="Position and Upvotes")

fig2
```

# Third Figure - we could do probably better to fit the model but I am going with linear assumptions
## (left) - third polynomial

```{r fig3a}
fig3a <- ggplot(data, aes(x=position, y=num_upvotes)) +
  theme_classic() +
  geom_point(alpha=0.4) +
  stat_smooth(method='lm', formula = y~poly(x,3)) +
  labs(x="Position in Thread", y="Number of Upvotes", title="Third Degree Polynomial")

fig3a
```

## (right) - taking log of number of upvotes 
```{r fig3b}
fig3b <- ggplot(data, aes(x=position, y=num_upvotes)) +
  theme_classic() +
  geom_point(alpha=0.4) +
  stat_smooth(method='lm', formula = y~log(x + 1)) +
  labs(x="Position in Thread", y="Number of Upvotes", title="Taking Log(x+1) on Number of Upvotes")

fig3b
```

## combined plot

```{r fig3}
fig3 <- ggarrange(fig3a, fig3b,
          ncol = 2, nrow = 1)
fig3
```

# Fourth Figure: number of non-stop words
## (left) - number of non-stop words and position

```{r fig31}
fig4a <- ggplot(data, aes(x=position, y=text_length)) +
  theme_classic() +
  geom_point(alpha=0.4) +
  geom_smooth(method=lm, se=TRUE) +
  labs(x="Position", y="Number of Non-stop Words", title="Position and Number of Non-stop Words")

fig4a
```

## (left) - number of non-stop words and upvotes

```{r fig4}
fig4b <- ggplot(data, aes(x=text_length, y=num_upvotes)) +
  theme_classic() +
  geom_point(alpha=0.4) +
  geom_smooth(method=lm, se=TRUE) +
  labs(x="Number of Non-stop Words", y="Number of Upvotes", title="Number of Non-stop Words and Upvotes")

fig4b
```

## combined plot

```{r fig4}
fig4 <- ggarrange(fig4a, fig4b,
          ncol = 2, nrow = 1)
fig4
```

# Fifth Figure: Upvote boxplot by participants
## with ID

```{r fig5_}
fig5_ <- ggplot(data, aes(x=reorder(name, -num_upvotes, FUN = median), y=num_upvotes)) +
  theme_classic() +
  geom_boxplot() +
  labs(x="Participant ID", y="Number of Upvotes", title="Upvotes by Participants") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

fig5_
```

## Without ID

```{r fig5}
fig5 <- ggplot(data, aes(x=reorder(name, -num_upvotes, FUN = median), y=num_upvotes)) +
  theme_classic() +
  geom_boxplot() +
  labs(x="Participant ID", y="Number of Upvotes", title="Upvotes by Participants") + 
  theme(axis.text.x = element_blank())

fig5
```

# Sixth Figure - did not made it in to the slides - Upvote boxplot by each workshop
```{r fig6}
data$workshop_date <- factor(data$workshop_date)

fig6 <- ggplot(data, aes(x=workshop_date, y=num_upvotes)) +
  theme_classic() +
  geom_boxplot() +
  labs(x="Workshop Date", y="Number of Upvotes", title="Upvotes by Workshop Date") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

fig6
```

# Linear Mixed model

```{r groupby}
# fitting lmm
lmm <- lmer(num_upvotes ~ position + text_length + (1|name) + (1|workshop_date), data = data, REML=FALSE)
summary(lmm)
```
